---
title: "Sales Insights"
author: "Michael C. Eleftheriades"
date: "7/9/2020"
output:
  powerpoint_presentation:
    reference_doc: test.pptx
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Insights:*not just new info but new data to be intepreted*

## Insights



- Not many purchases per day but  high on gross revenue
- Balanced distributions
- Steady sales




## New Data
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dygraphs)
options(dplyr.summarise.inform = FALSE)
library(plotly)
library(ggplot2)
library(tidyverse)
library(FRACTION)
#read sales file
clients <- read.csv("supermarket_sales.csv")
sum<-summary(clients$Quantity)
strDates <- c(clients$Date)
n<-nrow(clients)
data_frame <- tibble(strDates)
df <-data_frame[order(strDates),]
df2<-c(df)
#last date - first date = time frame 
time1 <- as.Date(df2$strDates[1], "%m/%d/%Y")
time2 <- as.Date(df2$strDates[n], "%m/%d/%Y")
time_diff<-difftime(time2, time1, units = "days") 
as_time_1<-as.numeric(time_diff, units = "days")
#gross
gross<-cumsum(clients$gross.income)
total_gross<-gross[length(gross)]
total_gross<-format(total_gross, digits=6, decimal.mark=",", big.mark= ".")
#sales
avg_sales<-n/as_time_1
avg_sales<-round(avg_sales)
#dates calculations
dates <- clients %>%
  group_by(Date, .drop = FALSE) %>%
  summarize(Purchases = n()) %>%
  mutate(Date = lubridate::mdy(Date)) %>%
  mutate(Date=format(Date,"%d-%m-%Y")) %>%
  arrange(desc(Purchases))

Dates<-dates$Date
Dates<-as.Date(dates$Date,"%d-%m-%Y" )
#per branch insights
df_branch <- clients %>%
  group_by(Branch, .drop = FALSE) %>%
  summarize(Count = n()) %>%
  mutate(Percentage = (Count / 1000)*100)
#per product line insights
prod_line<-clients %>% 
  group_by(Product.line, .drop= FALSE) %>% 
  count(Product.line )  %>% 
  mutate(Percentage = (n / 1000)*100)
#per gender insights
df_gender<- clients %>%
  group_by(Gender, .drop = FALSE) %>%
  summarize(counts = n()) %>% 
  mutate(Percentage = (counts / 1000)*100)
#per payment type insights
df_type <- clients %>%
  group_by(Payment, .drop = FALSE) %>%
  summarize(counts = n()) %>%
  mutate(Percentage = (counts / 1000)*100)
#per client type insights
client_type <- clients %>%
  group_by(Customer.type, .drop = FALSE) %>%
  summarize(Customers = n()) %>%
  mutate(Percentage = (Customers / 1000)*100)

```

- Sales on average  `r avg_sales`  a day but not less than `r min(dates$Purchases)` 
- Gross revenue of `r round(mean(clients$gross.income))`$  per purchase
- Balanced Ratios in every aspect:

    *  `r fra.m(mean(df_branch$Percentage)/100)` the sale per branch
    *  `r fra.m(mean(prod_line$Percentage)/100)` in product line choice per purchase
    *  `r fra.m(mean(df_gender$Percentage)/100)` if a client it's male or female 
    *  `r fra.m(mean(client_type$Percentage)/100)` if a client is a member or not
    *  `r fra.m(mean(df_type$Percentage)/100)` the preferance between payment methods
